Evaluation of the locality of the Mainline DHT

### 2014-05-29 paper.tex
updated paper

Distributed Hash Tables (DHT), is a well known and mature decentralized key-value store system. Mainline DHT, the larger DHT deployed world-wide, is commonly used for storing BitTorrent peers, but it works for arbitrary data as well. Even though, Mainline DHT specifications do not provide mechanism that encourage locality, we have done so by choosing a particular \textit{Proximity Neighbour Selection} routing policy that encourages locality by choosing routing nodes with the lower round-trip-time (RTT).

@@

The node IDs are assigned in a manner that ensures that nodes that are close in the network topology are close in the node ID space. Geographic Layout was explored as one technique to improve routing performance in CAN \cite{b4}. In one implementation, nodes measure the RTT between themselves and a set of landmark servers to compute the coordinates of the node in the CAN space.

@@

In figure \ref{fig:exp1-ids1-cache100} we see how caching seems to makes convergence to a better locality value, but repetitions of this same experiments shown mixed results. At this point we are not able to conclude that caching leads to better locality, at least in our 26 node DHT. However, caching seems to affect the patter on the routing table hops and latencies, compared with fig. \ref{fig:exp1,1-ids1-cache0}.

@@

All node's 120 most significant bits are the same, also an infohash with the same characteristics is inserted in the DHT and all the nodes perform periodic \texttt{GET\_PEERS} requests of this infohash.

@@

This experiment also uses crafted node IDs to force all node's ID being in the same bucket, from the lonely node point of view. We want to create a lot of bucket competition on the lonely node routing table and validate that the physically nearest node is always chosen.

@@

The lonely node is selected from this cluster since it will have plenty of nearby candidates to choose from. Figure \ref{fig:exp2,2-cache100-node39-original} illustrates the results of this experiment.

@@

Solely using the average number of hops may not be a good enough locality evaluator. A better one could be the average number of hops of the routing entries over the average number of hops to other nodes, ($\frac{avg(routing\_hops)}{avg(total\_hops}$), or even better, the potential optimal value over the current value. In short, making the values dependent of each node will give a better fit.

>>>>

Distributed Hash Tables (DHT) is a well known and mature decentralized key-value store system. Mainline DHT, the larger DHT deployed world-wide, is commonly used for storing BitTorrent peers, but it works for arbitrary data as well. Even though, Mainline DHT specifications do not provide mechanism that encourage locality, we have done so by choosing a particular \textit{Proximity Neighbour Selection} routing policy that encourages locality by choosing routing nodes with the lower round-trip-time (RTT).

@@

The node IDs are assigned in a manner that ensures that nodes that are close in the network topology are close in the node ID space. \textit{Geographic Layout} was explored as one technique to improve routing performance in CAN \cite{b4}. In one implementation, nodes measure the RTT between themselves and a set of landmark servers to compute the coordinates of the node in the CAN space.

@@

In figure \ref{fig:exp1-ids1-cache100} we see how caching seems to makes convergence to a better locality value, but repetitions of this same experiments show mixed results. At this point we are not able to conclude that caching leads to better locality, at least in our 26 node DHT. However, caching seems to affect the patter on the routing table hops and latencies, compared with fig. \ref{fig:exp1,1-ids1-cache0}.

@@

All node's ID 120 most significant bits are the same, also an infohash with the same characteristics is inserted in the DHT and all the nodes perform periodic \texttt{GET\_PEERS} requests of this infohash.

@@

This experiment also uses crafted node IDs to force all node's ID being in the same bucket from the lonely node point of view. We want to create a lot of bucket competition on the lonely node routing table and validate that the physically nearest node is always chosen.

@@

The lonely node is selected from this cluster since it have plenty of nearby candidates to choose from. Figure \ref{fig:exp2,2-cache100-node39-original} illustrates the results of this experiment.

@@

Solely using the average number of hops may not be a good enough locality evaluator. A better one could be the average number of hops of the routing entries over the average number of hops to other nodes, ($\frac{avg(routing\_hops)}{avg(total\_hops}$). Or even better, the potential optimal value over the current value. In short, making the values dependent of each node vision of the network will give a better fit.
